Tugas Pak Farit

### 2024-05-05 Project/Tugas Pak Farit.Rmd
Update

```{r}
sapply(lapply(norm_samples, mean), function(x) x)
sapply(lapply(unif_samples, mean), function(x) x)
sapply(lapply(exp_samples, mean), function(x) x)

@@

```

>>>>

```{r}
mean_norm <- sapply(lapply(norm_samples, mean), function(x) x)
mean_unif <- sapply(lapply(unif_samples, mean), function(x) x)
mean_exp  <- sapply(lapply(exp_samples, mean), function(x) x)

@@

# Statistik sd sample
norm_s <- c()
norm_s[1] <- norm_sd /sqrt(sample_n[[1]])
norm_s[2] <- norm_sd /sqrt(sample_n[[2]])
norm_s[3] <- norm_sd /sqrt(sample_n[[3]])

cat("# Pendugaan SK Normal #",
    "\n        Nilai tengah      Standar Deviasi",
    "\nn=10  :",mean_norm[1], "    \u00B1   ", norm_s[1],
    "\nn=30  :",mean_norm[2], "     \u00B1   ", norm_s[2],
    "\nn=100 :",mean_norm[3], "    \u00B1   ", norm_s[3])
```
